Learning words by recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
more figures
fix sectioning
more text

\subsection{Statistical cross-situational word learning}

Even very young children can learn words from individually ambiguous situations, e.g. where multiple words are spoken and multiple objects are present \cite{smith2008}. While no individual situation gives away the mapping, the pattern of co-occurrences between words and objects allows for learning. Our current model reproduces this pattern of results, converging to correct lexical mappings from ambiguous evidence.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures/horn-emergence-0.pdf}
\includegraphics[width=0.48\textwidth]{figures/horn-emergence-1.pdf}
\caption{\label{fig:horn} Simulations.}
\end{figure}

>>>>

% \subsection{Statistical cross-situational word learning}

% Even very young children can learn words from individually ambiguous situations, e.g. where multiple words are spoken and multiple objects are present \cite{smith2008}. While no individual situation gives away the mapping, the pattern of co-occurrences between words and objects allows for learning. Our current model reproduces this pattern of results, converging to correct lexical mappings from ambiguous evidence.

@@

\begin{SCfigure}
\centering
\includegraphics[width=0.5\textwidth]{figures/horn-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/horn-emergence-1.pdf}
\caption{\label{fig:horn} Simulations.}
\end{SCfigure}
